%%
%% Copyright (c) 2018-2019 Weitian LI <wt@liwt.net>
%% CC BY 4.0 License
%%
%% Created: 2018-04-11
%%

% Chinese version
\documentclass[zh]{resume}

% Adjust icon size (default: same size as the text)
\iconsize{\Large}

% File information shown at the footer of the last page
\fileinfo{%
  \faCopyright{} 2018--2020, Weitian LI \hspace{0.5em}
  \creativecommons{by}{4.0} \hspace{0.5em}
  \githublink{liweitianux}{resume} \hspace{0.5em}
  \faEdit{} \today
}

\name{Haoxuan}{Han}

\keywords{Rust, Linux, Programming, Python, C, Shell, Bare matel}

% \tagline{\icon{\faBinoculars}} <position-to-look-for>}
% \tagline{<current-position>}

% \photo{<height>}{<filename>}

\profile{
  \mobile{176-6409-4001}
  \email{hhx.xxm@gmail.com}
  \github{Oyami-Srk} \\
  \university{Qilu Institute of Technology}
  \degree{Computer Science \textbullet Bachelor}
  \birthday{2001-01-25}
  \address{Qingdao}
  % Custom information:
  % \icontext{<icon>}{<text>}
  % \iconlink{<icon>}{<link>}{<text>}
}

\begin{document}
\makeheader

%======================================================================
% Summary & Objectives
%======================================================================
{\onehalfspacing\hspace{2em}%
I'm a Computer Science undergraduate with a profound passion for delving into computer fundamentals and operating systems. Enthusiastic about operating system technologies, Have written kernels for x86 and RISC-V platforms for learning. With years of experience using Linux, I possess adept skills in Linux Shell, Python, C language, and Rust language, along with a certain level of expertise in embedded software development. Embracing the spirit of open source, I have contributed to several open source projects on my \link{https://github.com/Oyami-Srk}{GitHub}, in addition to sharing personal projects. Proficient in English, I exhibit exceptional reading and writing abilities, enabling smooth communication and documentation comprehension. 
Backed by extensive experience in low-level computer understanding and bare-metal development, I am capable of independently undertaking design, development, and debugging of a kernel-level functionalities. Equipped with embedded software development capabilities, I can engineer stable embedded software solutions. Adept in utilizing tools like Git, Shell, and CMake, I possess experience with many popular IDEs. My proficiency with the Linux operating system extends to developing foundational tools, enabling me to craft scripts and programs tailored to specific requirements.

\par}


%======================================================================
%\sectionTitle{技能和语言}{\faWrench}
%======================================================================
%\begin{competences}
%  \comptence{编程语言}{%
%    C, Shell, Python, Rust, Typescript
%  }
%  %\comptence{工具}{%
%  %  ZSH, SSH, Git, Make, CMake, Vim
%  %}
%  \comptence{\icon{\faLanguage} 语言}{
%    \textbf{英语} --- 读写（优良），听说（日常交流）
%  }
%\end{competences}

%======================================================================
\sectionTitle{Education Background}{\faGraduationCap}
%======================================================================
\begin{educations}
  \education%
    {2020.09}%
    [2024.06]%
    {Qilu Institute of Technology}%
    {Computer and Information engineering insitute}%
    {Computer Science}%
    {Bachelor (Undergraduate)}
\end{educations}

%======================================================================
%\sectionTitle{计算机技能}{\faCogs}
%======================================================================
%\begin{itemize}
%	\item 熟练掌握以下编程语言和技术：C, Shell, Python, Rust, Typescript。
%	\item 能够熟练使用英文，具有优秀的读写能力，能够使用英文进行日常交流、阅读文档。
%	% \item 优秀的学习能力，热爱新技术，自学能力强。
%	\item 有充分的计算机底层、裸机开发的经验，能够独立完成操作系统内核级别的设计与开发。%，对Linux系统内核原理有深入的了解。
%	\item 具备一定的嵌入式软件开发能力，可以开发出稳定的嵌入式软件。
%	\item 熟练使用Linux操作系统，具备开发基础工具的能力，可以根据需求编写特定功能的脚本、程序等。
%	\item 熟练使用Git、Shell、CMake等工具，对主流的集成开发环境有丰富的使用经验。
%	% \item 能够快速上手新技术、新框架、新语言，可以对特定需求进行快速开发。
%\end{itemize}


%======================================================================
\sectionTitle{Projects}{\faCode}
%======================================================================
\begin{itemize}
	\item \link{https://gitee.com/BookOS/nxos/tree/proj-3-virtio/}{\texttt{VirtIO Driver Implementation based on NXOS Kernel}}:
	(C)
Developed a series of VirtIO drivers for the NXOS kernel, as part of the "OSPP 2023" initiative. This ongoing project involves implementing VirtIO 1.2 specification-based drivers within the NXOS kernel, including VirtIO Over PCI Bus and VirtIO Over MMIO. The drivers encompass a various regular virtio devices driver. Throughout the project's execution, I also addressed and rectified specific code errors within the NXOS codebase.
\end{itemize}

\begin{itemize}
	\item \link{https://github.com/Oyami-Srk/OmochaOS/tree/backup-main-cmake-2022}{\texttt{OmochaOS}}:
	(C, CMake)
Toy kernel for study of x86 development, with a microkernel architecture. Successfully implemented drivers for essential components such as HPET, PCI, APIC, and AHCI. Additionally, a modular framework to ensure extensibility and flexibility within the system has been implemented.
	\item \link{https://github.com/Oyami-Srk/MFTT-RISCV} {\texttt{MFTT-RISCV}}:
	(C, CMake)
Kernel for the RISC-V for the Operating System Design Competition. Employing a macrokernel architecture, I achieved the following milestones: SMP, Buddy  page allocator, RB Tree based slab allocator, CoW Fork, Device Tree Framework for FDT, Read-only FAT32 Filesystem, parial POSIX system calls including execve, dup, and pipe, compatibility with a subset of Linux system calls, The system is support QEMU and K210, along with virtio-mmio and virtio-disk drivers for device communication. This endeavor showcases a comprehensive understanding of operating system design and kernel-level development within the RISC-V architecture.
	\item \link{https://github.com/Oyami-Srk/SelfServiceCarWashing} {\texttt{SelfServiceCarWashing}}:
	(C)
The embedded part of a Self-service Car Washing machine based on STM32F4 and LVGL. Along with network control and data transmission functionality.
	\item \link{https://github.com/Oyami-Srk/AiR} {\texttt{AiR}}:
	(C, C++)
The AiR Air Quality Monitoring System based on ESP32. With MQTT, HTTP API and HTTP Frontend support.
\end{itemize}

\begin{itemize}
%Python
	\item \link{https://github.com/Oyami-Srk/RISCV-GDB-Paging} {\texttt{RISCV-GDB-Paging}}:
	(Python, Scheme)
GDB Script for debugging Paging mechanism SV39/SV48 for RISC-V architecture on QEMU. Using Python and Scheme Lisp for the implementation.
	\item \link{https://github.com/Oyami-Srk/OmegaGomoku} {\texttt{OmegaGomoku}}:
	(Python)
Developed a Gomoku AI using PyTorch and DQN algorithm. Optimized DQN reward calculation. Achieved moderate AI performance after 100k training games. Outperformed MiniMax with 95\% max win rate and 50\% average win rate at 2-level search depth.

	\item Safety Training Platform based on Django, Vue and Wechat Mini Program:
	(Python、Typescript)
Personal freelance project: Developed an online safety training platform. Featuring video learning with periodic face verification, quiz assessments, and comment. Backend built with Django and Django REST Framework; admin panel using Vue and Vue-pure-admin template. Providing two trainee front-end options: Vue-based and WeChat Mini Program, both offering the same functionality.

\end{itemize}

\begin{itemize}
%Rust
	\item \link{https://github.com/Oyami-Srk/Rust-shunting\_yard} {\texttt{Rust-shunting\_yard}}:
	(Rust)
Expression evaluation tool written in Rust using the Shunting Yard algorithm, equipped with function definition capabilities.
	\item \link{https://github.com/Oyami-Srk/rust-headless-chrome/tree/resp-handler-dereg} {\texttt{Rust-headless-chrome(Code contribution)}}:
	(Rust)
	Contributed code to the Chrome DevTools Protocol implementation API in Rust, enhancing and refining certain API application methods.Additionally, addressed errors within the code generation tool (\link{https://github.com/Oyami-Srk/auto\_generate\_cdp}{\texttt{auto\_generate\_cdp}}) to improve the overall functionality and reliability of the project.
	\item \link{https://github.com/Oyami-Srk/shirodl} {\texttt{ShiroDL}}:
	(Rust)
Asynchronous concurrent small-file download library in Rust, designed for versatility and extensibility. Includes a command-line program for batch downloading small files.

\end{itemize}


%======================================================================
\sectionTitle{Awards and Certificates}{\faTrophy}
%======================================================================
\begin{itemize}
  \item\link{https://qvq.moe:5001/public/imgs/2018-GoogleCodeIn\%E9\%AB\%98\%E4\%B8\%AD.jpg}{\texttt{Google Code-in 2017}}
	\item\link{https://qvq.moe:5001/public/imgs/2020-\%E5\%A4\%96\%E7\%A0\%94\%E7\%A4\%BE\%E5\%9B\%BD\%E6\%9D\%90\%E6\%9D\%AF\%E5\%85\%A8\%E5\%9B\%BD\%E8\%8B\%B1\%E8\%AF\%AD\%E9\%98\%85\%E8\%AF\%BB\%E5\%A4\%A7\%E8\%B5\%9B\%E5\%B1\%B1\%E4\%B8\%9C\%E7\%9C\%81\%E5\%A4\%8D\%E8\%B5\%9B-\%E4\%B8\%89\%E7\%AD\%89\%E5\%A5\%96.jpg} {\texttt{2020\enquote{FLTRP·ETIC Cup}English Reading Contest\ Shandong Provincial Final \ Third Award}}
	\item\link{https://qvq.moe:5001/public/imgs/2021-\%E4\%B8\%AD\%E5\%9B\%BD\%E5\%A4\%A7\%E5\%AD\%A6\%E7\%94\%9F\%E8\%AE\%A1\%E7\%AE\%97\%E6\%9C\%BA\%E8\%AE\%BE\%E8\%AE\%A1\%E5\%A4\%A7\%E8\%B5\%9B\%E5\%B1\%B1\%E4\%B8\%9C\%E7\%9C\%81\%E7\%BA\%A7\%E8\%B5\%9B-\%E4\%B8\%89\%E7\%AD\%89\%E5\%A5\%96.jpg} {\texttt{2021 14th Chinese Collegiate Computing Competition\ Shandong Provincial\ Third Award}}
	\item\link{https://qvq.moe:5001/public/imgs/2021-\%E5\%85\%A8\%E5\%9B\%BD\%E5\%A4\%A7\%E5\%AD\%A6\%E7\%94\%9F\%E8\%8B\%B1\%E8\%AF\%AD\%E7\%AB\%9E\%E8\%B5\%9BC\%E7\%B1\%BB-\%E4\%BA\%8C\%E7\%AD\%89\%E5\%A5\%96.jpg} {\texttt{2021 3rd National College Computer Ability Challenge\ Program design-C++Easten China area\ Excellence Award}}
	\item\link{https://qvq.moe:5001/public/imgs/2021-\%E5\%B1\%B1\%E4\%B8\%9C\%E7\%9C\%81\%E5\%A4\%A7\%E5\%AD\%A6\%E7\%94\%9F\%E7\%94\%B5\%E5\%AD\%90\%E4\%B8\%8E\%E4\%BF\%A1\%E6\%81\%AF\%E6\%8A\%80\%E6\%9C\%AF\%E5\%BA\%94\%E7\%94\%A8\%E5\%A4\%A7\%E8\%B5\%9B-\%E4\%BA\%8C\%E7\%AD\%89\%E5\%A5\%96.jpg} {\texttt{\enquote{赛冠杯}8th Shandong Provincial College Students' Electronic and Information Technology Application Competition\ Second Award}}
	\item\link{https://qvq.moe:5001/public/imgs/2022-\%E4\%B8\%AD\%E5\%9B\%BD\%E5\%A4\%A7\%E5\%AD\%A6\%E7\%94\%9F\%E8\%AE\%A1\%E7\%AE\%97\%E6\%9C\%BA\%E8\%AE\%BE\%E8\%AE\%A1\%E5\%A4\%A7\%E8\%B5\%9B\%E7\%9C\%81\%E4\%BA\%8C\%E7\%AD\%89\%E5\%A5\%96.jpg} {\texttt{2022 15th Chinese Collegiate Computing Competition\ Shandong Provincial\ Second Award}}
	\item\link{https://qvq.moe:5001/public/imgs/2022-\%E6\%93\%8D\%E4\%BD\%9C\%E7\%B3\%BB\%E7\%BB\%9F\%E8\%AE\%BE\%E8\%AE\%A1\%E5\%88\%9D\%E8\%B5\%9B\%E4\%BC\%98\%E8\%83\%9C\%E5\%A5\%96.jpg} {\texttt{2022 Computer System Development Capability Competition - Kernel Design Competition\ 
Preliminary Excellence Award}}
	\item\link{https://qvq.moe:5001/public/imgs/2022-\%E8\%93\%9D\%E6\%A1\%A5\%E6\%9D\%AF\%E5\%9B\%BD\%E8\%B5\%9BB\%E7\%BB\%84-\%E4\%B8\%89\%E7\%AD\%89\%E5\%A5\%96.jpg} {\texttt{13rd Blue Bridge Cup\ Shandong Provincal C/C++\ College B Group\ First Award}}
	\item\link{https://qvq.moe:5001/public/imgs/2022-\%E8\%93\%9D\%E6\%A1\%A5\%E6\%9D\%AF\%E5\%9B\%BD\%E8\%B5\%9BB\%E7\%BB\%84-\%E4\%B8\%89\%E7\%AD\%89\%E5\%A5\%96.jpg} {\texttt{13rd Blue Bridge Cup\ National Finals C/C++\ College B Group\ Third Award}}
	\item\link{https://qvq.moe:5001/public/imgs/\%E8\%BD\%AF\%E4\%BB\%B6\%E8\%91\%97\%E4\%BD\%9C\%E6\%9D\%83\%E7\%99\%BB\%E8\%AE\%B0\%E8\%AF\%81\%E4\%B9\%A6-\%E7\%A9\%BA\%E6\%B0\%94\%E8\%B4\%A8\%E9\%87\%8F\%E6\%A3\%80\%E6\%B5\%8B\%E7\%B3\%BB\%E7\%BB\%9F.jpg} {\texttt{National Copyright Administration of China\  Computer software copyright registration certificate\ AiR Air Quality Monitoring System}}
\end{itemize}


\end{document}
