%%
%% Copyright (c) 2018-2019 Weitian LI <wt@liwt.net>
%% CC BY 4.0 License
%%
%% Created: 2018-04-11
%%

\hbadness=99999 

% English version
\documentclass{resume}

% Adjust icon size (default: same size as the text)
\iconsize{\Large}

% File information shown at the footer of the last page
\fileinfo{%
  \faCopyright{} 2018--2020, Weitian LI \hspace{0.5em}
  \creativecommons{by}{4.0} \hspace{0.5em}
  \githublink{liweitianux}{resume} \hspace{0.5em}
  \faEdit{} \today
}

\name{HaoXuan}{Han}

\keywords{Rust, Linux, Programming, Python, C, Shell, Bare matel}

% \tagline{\icon{\faBinoculars}} <position-to-look-for>}
% \tagline{<current-position>}

% \photo{<height>}{<filename>}

\profile{
  \mobile{176-6409-4001}
  \email{hhx.xxm@gmail.com}
  \github{Oyami-Srk} \\
  \university{Qilu Institute of Technology}
  \degree{Computer Science \textbullet Bachelor}
  \birthday{2001-01-25}
  \address{Qingdao}
  % Custom information:
  % \icontext{<icon>}{<text>}
  % \iconlink{<icon>}{<link>}{<text>}
}

\begin{document}
\makeheader

%======================================================================
% Summary & Objectives
%======================================================================
{\onehalfspacing
\hspace{2em}
I have dived into in low-level and kernel developments. Passionate about operating system and have developed kernels for x86 and RISC-V architectures. 
I'm familiar with the Linux kernel and system, and with experience in embedded development.

\onehalfspacing
\hspace{2em}
With extensive experience in low-level and bare-metal development, I am capable of independently designing, developing, and debugging OS Kernel. I have a rich experience in many developing toolkits.
I am enthusiastic about the open-source community and have open-sourced various personal projects on \link{https://github.com/Oyami-Srk}{GitHub}, and also contributed to some open-source projects.
\par}


\sectionTitle{Skills}{\faWrench}
\begin{competences}[7em]
  \comptence{Development}{%
    C, Shell, Python, Rust, Typescript, Git, CMake, ……
  }
  \comptence{\icon{\faLanguage} Language}{
    \textbf{English} --- Reading/Writing (Excellent), Listening/Speaking (Good), Being used to read/write documents in English.
  }
\end{competences}

%======================================================================
\sectionTitle{Education}{\faGraduationCap}
%======================================================================
\begin{educations}
  \education%
    {2020.09}%
    [2024.06]%
    {Qilu Institute of Technology}%
    {Computer and Information engineering insitute}%
    {Computer Science}%
    {Bachelor (Undergraduate)}
\end{educations}


%======================================================================
\sectionTitle{Personal Projects}{\faCode}
%======================================================================
\begin {projects}
	\project{2023.7}[Present][https://gitee.com/BookOS/nxos/tree/proj-3-virtio/]{VirtIO Drivers implementation based on NXOS Kernel}{
		Project of \link{https://summer-ospp.ac.cn/org/prodetail/238070164?lang=zh&list=pro}{OSPP 2023}, implement VirtIO Drivers for NXOS kernel, is currently ongoing.
		\begin{itemize}
			\item Implemented VirtIO Over PCI Bus and VirtIO Over MMIO
			\item Implemented various VirtIO devices, such as Net, Block, Input, Sound, etc.
			\item Fixed Bugs in NXOS Kernel codebase
			\item Archived compatibility to error implementations beyond specification through studying the sources of Linux kernel and QEMU
		\end{itemize}
	}[C,VirtIO,QEMU,Low-level development,Driver developement]

	\project{2023.4}[2023.7]{Safety Training Online Platform}{
		Personal freelance project. Archived a online video training platoform with features of online training, face recognition, quiz tests and comments.
		\begin{itemize}
			\item Using Django and Django REST Framework as backend implementation
			\item Using Vue3.0 and Vue-Pure-Admin framework for administration panel
			\item Archived same functionality via Vue and Wechat mini program for trainee frontend
		\end{itemize}
	}[Python,Django,Django REST Framework,Vue,Full stack development]

	\project{2022.5}[2022.7][https://github.com/Oyami-Srk/MFTT-RISCV]{OS Kernel based on RISC-V Architecture}{
		Project for \link{https://os.educg.net/\#/oldDetail?name=2022\%E5\%85\%A8\%E5\%9B\%BD\%E5\%A4\%A7\%E5\%AD\%A6\%E7\%94\%9F\%E8\%AE\%A1\%E7\%AE\%97\%E6\%9C\%BA\%E7\%B3\%BB\%E7\%BB\%9F\%E8\%83\%BD\%E5\%8A\%9B\%E5\%A4\%A7\%E8\%B5\%9B\%E6\%93\%8D\%E4\%BD\%9C\%E7\%B3\%BB\%E7\%BB\%9F\%E8\%AE\%BE\%E8\%AE\%A1\%E8\%B5\%9B-\%E5\%86\%85\%E6\%A0\%B8\%E5\%AE\%9E\%E7\%8E\%B0\%E8\%B5\%9B}{Kernel Design Competition}, a kernel based on RISC-V 64 architecture, a macrokernel design. Communicate with hardware through SBI and therefore the portability and universality could be archived.
		\begin{itemize}
			\item Archived SMP multi-processor via spinlock and sleeplock
			\item Archived Buddy Page Allocator and RB-Tree based Slab objects allocator
			\item Implemented CoW Fork to improve performance
			\item Archived support of Flatten Device Tree along with extensible driver framework
			\item Archived some generic POSIX syscalls like Execve, dup, pipe and with compatibility to some Linux syscalls
			\item Support QEMU and K210, and implemented virtio-mmio/virtio-disk for QEMU
			\item Developed \link{https://github.com/Oyami-Srk/RISCV-GDB-Paging} {\texttt{RISCV-GDB-Paging}} for debugging VS39/SV48 paging information for RISC-V on QEMU. Written in Python and Scheme Lisp
		\end{itemize}
	}[C,CMake,Low-level developement,Kenrel developement,RISC-V,GDB,Python]

	\project{2021.10}[2022.3][https://github.com/Oyami-Srk/SelfServiceCarWashing]{Self Service Car Washing Embedded Software}{
		Embedded part of Self Service Car Washing solutions, this project archived the terminal electrical controlling and user-end GUI.
		\begin{itemize}
			\item As project manager, I coordinated developers in other parts and collaborated with partner companies
			\item Using STM32F4 as MCU and developed through STM32 HAL
			\item Ported LVGL using DMA2D for a high performance, decoupling the LVGL GUI from embedded functionality for easier debugging and development
			\item Communicate with LTE IoT modules and ESP32 via AT commands, enabling interaction with server-side systems
			\item Implemented configurating from PC through USB-FS and FATFS
			\item Employed FreeRTOS as the embedded operating system, using tasks to handle different sub-procedures
		\end{itemize}
	}[C,STM32,LVGL,FreeRTOS,Embedded developement]
\end {projects}

\sectionTitle{Other Personal Projects}{\faCode}
\begin{itemize}
	\item \simpleProject[https://github.com/Oyami-Srk/OmochaOS/tree/backup-main-cmake-2022]{OmochaOS}{
		Toy kernel for study of x86 development, with a microkernel architecture. Successfully implemented drivers for essential components such as HPET, PCI, APIC, and AHCI. Additionally, a modular framework to ensure extensibility and flexibility within the system has been implemented.
	}[C,CMake,Kernel development,Low-level developement]
	\item \simpleProject[https://github.com/Oyami-Srk/AiR]{AiR Air Quality Monitoring System}{
		The AiR Air Quality Monitoring System based on ESP32. With MQTT, HTTP API and HTTP Frontend support in network and also with display support in onboard LCD.
	}[C,Embedded developement,FreeRTOS,ESP32]
	\item \simpleProject[https://github.com/Oyami-Srk/OmegaGomoku]{OmegaGomoku}{
		Developed a Gomoku AI using PyTorch and DQN algorithm. Optimized DQN reward calculation. Achieved moderate AI performance after 100k training games. Outperformed MiniMax with 95\% max win rate and 50\% average win rate at 2-level search depth.
		Report: \link{https://blog.qvq.moe/OmegaGomoku/Report/\%E4\%BA\%BA\%E5\%B7\%A5\%E6\%99\%BA\%E8\%83\%BD\%E8\%AF\%BE\%E7\%A8\%8B\%E6\%8A\%A5\%E5\%91\%8A.pdf}{Click Here}
	}[Python,PyTorch,DQN,Machine Learning,Deep Learning]
	\item \simpleProject[https://github.com/Oyami-Srk/Rust-shunting\_yard]{Rust-shunting\_yard}{
		Expression evaluation tool written in Rust using the Shunting Yard algorithm, equipped with function definition capabilities.
	}[Rust,Algorithm]
	\item \simpleProject[https://github.com/Oyami-Srk/rust-headless-chrome/tree/resp-handler-dereg]{Rust-headless-chrome(Code contribution)}{
		Contributed code to the Chrome DevTools Protocol implementation API in Rust, enhancing and refining certain API application methods. Additionally, fixed errors within the code generation tool (\link{https://github.com/Oyami-Srk/auto\_generate\_cdp}{\texttt{auto\_generate\_cdp}}) to solve the functionality issue of the projecct.
	}[Rust,Library,Chrome DevTools]
	\item \simpleProject[https://github.com/Oyami-Srk/shirodl]{ShiroDL}{
		Asynchronous concurrent small-file download library in Rust, designed for versatility and extensibility. Includes a command-line program for batch downloading small files.
	}[Rust,Library,Tool developement]
\end{itemize}

%======================================================================
\sectionTitle{Awards and Certificates}{\faTrophy}
%======================================================================
\begin{itemize}
  \item\link{https://qvq.moe:5001/public/imgs/2018-GoogleCodeIn\%E9\%AB\%98\%E4\%B8\%AD.jpg}{\texttt{Google Code-in 2017}}
	\item\link{https://qvq.moe:5001/public/imgs/2020-\%E5\%A4\%96\%E7\%A0\%94\%E7\%A4\%BE\%E5\%9B\%BD\%E6\%9D\%90\%E6\%9D\%AF\%E5\%85\%A8\%E5\%9B\%BD\%E8\%8B\%B1\%E8\%AF\%AD\%E9\%98\%85\%E8\%AF\%BB\%E5\%A4\%A7\%E8\%B5\%9B\%E5\%B1\%B1\%E4\%B8\%9C\%E7\%9C\%81\%E5\%A4\%8D\%E8\%B5\%9B-\%E4\%B8\%89\%E7\%AD\%89\%E5\%A5\%96.jpg} {\texttt{2020\enquote{FLTRP·ETIC Cup}English Reading Contest\ Shandong Provincial Final \ Third Award}}
	\item\link{https://qvq.moe:5001/public/imgs/2021-\%E4\%B8\%AD\%E5\%9B\%BD\%E5\%A4\%A7\%E5\%AD\%A6\%E7\%94\%9F\%E8\%AE\%A1\%E7\%AE\%97\%E6\%9C\%BA\%E8\%AE\%BE\%E8\%AE\%A1\%E5\%A4\%A7\%E8\%B5\%9B\%E5\%B1\%B1\%E4\%B8\%9C\%E7\%9C\%81\%E7\%BA\%A7\%E8\%B5\%9B-\%E4\%B8\%89\%E7\%AD\%89\%E5\%A5\%96.jpg} {\texttt{2021 14th Chinese Collegiate Computing Competition\ Shandong Provincial\ Third Award}}
	\item\link{https://qvq.moe:5001/public/imgs/2021-\%E5\%85\%A8\%E5\%9B\%BD\%E5\%A4\%A7\%E5\%AD\%A6\%E7\%94\%9F\%E8\%8B\%B1\%E8\%AF\%AD\%E7\%AB\%9E\%E8\%B5\%9BC\%E7\%B1\%BB-\%E4\%BA\%8C\%E7\%AD\%89\%E5\%A5\%96.jpg} {\texttt{2021 3rd National College Computer Ability Challenge\ Program design-C++Easten China area\ Excellence Award}}
	\item\link{https://qvq.moe:5001/public/imgs/2021-\%E5\%B1\%B1\%E4\%B8\%9C\%E7\%9C\%81\%E5\%A4\%A7\%E5\%AD\%A6\%E7\%94\%9F\%E7\%94\%B5\%E5\%AD\%90\%E4\%B8\%8E\%E4\%BF\%A1\%E6\%81\%AF\%E6\%8A\%80\%E6\%9C\%AF\%E5\%BA\%94\%E7\%94\%A8\%E5\%A4\%A7\%E8\%B5\%9B-\%E4\%BA\%8C\%E7\%AD\%89\%E5\%A5\%96.jpg} {\texttt{\enquote{Sai Guan Cup}8th Shandong Provincial College Students' Electronic and Information Technology Application Competition\ Second Award}}
	\item\link{https://qvq.moe:5001/public/imgs/2022-\%E4\%B8\%AD\%E5\%9B\%BD\%E5\%A4\%A7\%E5\%AD\%A6\%E7\%94\%9F\%E8\%AE\%A1\%E7\%AE\%97\%E6\%9C\%BA\%E8\%AE\%BE\%E8\%AE\%A1\%E5\%A4\%A7\%E8\%B5\%9B\%E7\%9C\%81\%E4\%BA\%8C\%E7\%AD\%89\%E5\%A5\%96.jpg} {\texttt{2022 15th Chinese Collegiate Computing Competition\ Shandong Provincial\ Second Award}}
	\item\link{https://qvq.moe:5001/public/imgs/2022-\%E6\%93\%8D\%E4\%BD\%9C\%E7\%B3\%BB\%E7\%BB\%9F\%E8\%AE\%BE\%E8\%AE\%A1\%E5\%88\%9D\%E8\%B5\%9B\%E4\%BC\%98\%E8\%83\%9C\%E5\%A5\%96.jpg} {\texttt{2022 Computer System Development Capability Competition - Kernel Design Competition\ 
Preliminary Excellence Award}}
	\item\link{https://qvq.moe:5001/public/imgs/2022-\%E8\%93\%9D\%E6\%A1\%A5\%E6\%9D\%AF\%E5\%9B\%BD\%E8\%B5\%9BB\%E7\%BB\%84-\%E4\%B8\%89\%E7\%AD\%89\%E5\%A5\%96.jpg} {\texttt{13rd Blue Bridge Cup\ Shandong Provincal C/C++\ College B Group\ First Award}}
	\item\link{https://qvq.moe:5001/public/imgs/2022-\%E8\%93\%9D\%E6\%A1\%A5\%E6\%9D\%AF\%E5\%9B\%BD\%E8\%B5\%9BB\%E7\%BB\%84-\%E4\%B8\%89\%E7\%AD\%89\%E5\%A5\%96.jpg} {\texttt{13rd Blue Bridge Cup\ National Finals C/C++\ College B Group\ Third Award}}
	\item\link{https://qvq.moe:5001/public/imgs/\%E8\%BD\%AF\%E4\%BB\%B6\%E8\%91\%97\%E4\%BD\%9C\%E6\%9D\%83\%E7\%99\%BB\%E8\%AE\%B0\%E8\%AF\%81\%E4\%B9\%A6-\%E7\%A9\%BA\%E6\%B0\%94\%E8\%B4\%A8\%E9\%87\%8F\%E6\%A3\%80\%E6\%B5\%8B\%E7\%B3\%BB\%E7\%BB\%9F.jpg} {\texttt{National Copyright Administration of China\  Computer software copyright registration certificate\ AiR Air Quality Monitoring System}}
\end{itemize}


\end{document}

